|

### 2025-05-06 doc/paper.qmd
Formatted equation with Quarto label for referencing

# Introduction {#sec-introduction}
This project serves as a template-based example for conducting and documenting reproducible empirical accounting research. It leverages the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) and builds upon the methodological foundations of the Corporate Decision-Making and Quantitative Analysis course, as well as the Accounting Reading Group course, which explored archival and non-archival research methods. To support future empirical thesis projects, this template was adapted and further developed specifically for students at the School of Business and Economics at Humboldt-Universität zu Berlin—particularly those affiliated with the Institute of Accounting and Auditing and the Finance Group.

Following prior assignments on audit market concentration and financial reporting effects (e.g., @graham_economic_2005), this project focuses on the informativeness of quarterly earnings announcements. Specifically, it replicates and extends the study by @ball_how_2008, which examines whether earnings announcements contribute new information to markets or merely confirm what is already known—contributing to the long-standing discussion on market efficiency and the valuation versus contracting roles of accounting.

@@

Specifically, buy-and-hold return over the three-day event window, that measures the stock’s reaction only to earnings news, is computed as given below:
$$
\begin{aligned}
BHR_{\text{event}} &= (1 + R_{t_1}) (1 + R_{t_2}) \dots (1 + R_{t_T}) - 1,
\\
\text{where } R_t & \text{ is the daily return and } T \text{ is the total trading days in a year.}
\end{aligned}
$$

>>>>

# Introduction {#sec-introduction}
This project serves as a template-based example for conducting and documenting reproducible empirical accounting research. It leverages the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) and builds upon the methodological foundations of the Corporate Decision-Making and Quantitative Analysis course, as well as the Accounting Reading Group course, which explored archival and non-archival research methods. To support future empirical thesis projects, this template was adapted and further developed specifically for students at the School of Business and Economics at Humboldt-Universität zu Berlin—particularly those affiliated with the Institute of Accounting and Auditing and the Finance Group. The template was developed in adherence to the formal formatting and content guidelines of the School of Business and Economics, and in particular, those of the Institute of Accounting and Auditing.

The template project showcases a research on audit market concentration and financial reporting effects (e.g., @graham_economic_2005), and focuses on the informativeness of quarterly earnings announcements. Specifically, it replicates and extends the study by @ball_how_2008, which examines whether earnings announcements contribute new information to markets or merely confirm what is already known—contributing to the long-standing discussion on market efficiency and the valuation versus contracting roles of accounting.

@@

Specifically, buy-and-hold return over the three-day event window, that measures the stock’s reaction only to earnings news, is computed as shown in @eq-bhr_event:
$$
\begin{aligned}
BHR_{\text{event}} &= (1 + R_{t_1}) (1 + R_{t_2}) \dots (1 + R_{t_T}) - 1,
\\
\text{where } R_t & \text{ is the daily return and } T \text{ is the total trading days in a year.}
\end{aligned}
$$ {#eq-bhr_event}
